\section{Question 7}

    \subsection{Difference between polling server and deferrable server}
        
        A polling server polls aperiodic tasks at a fixed period, at each poll a specific amount of execution capacity is provided for use if there is any aperiodic task request but it will lose its execution capacity if there are no aperiodic task requests. On the other hand a deferrable server will not lose its capacity if there are no aperiodic task requests. In the case of the polling server an aperiodic task that arrives after a poll has been made will have to wait until the next poll to be executed. In the case of the deferrable server an aperiodic task that arrives after a poll has been made will be executed immediately, given that it is the highest priority task ready at that instance, since the execution capacity has been retained.\\

    \subsection{Does Deferrable Server used together with Rate monotonic increase or decrease the Rate Monotonic schedulability bound?}
        
        If the $U_S$ (server utility factor) is less than $0.4$ the RM bound is decreased. If the $U_S$ is greater than $0.4$ the RM bound is increased.\\

    \subsection{Main difference between Total Bandwidth Server and Constant Bandwidth Server?}

        A Total Bandwidth Server (TBS) is a dynamic server which is used to schedule aperiodic task requests. It assigns each aperiodic request a specific deadline such that $U_P + U_S <= 1$ where $U_S$ is the processor utilization factor of the aperiodic task set. Since the TBS is used with EDF scheduling the each deadline will be met as long as the statement is true and each task is executed as expected. The deadline is assigned using the formula: $d_k = a_k + \frac{C_k}{U_s}$ or $d_k = max(a_k, d_{k-1}) + \frac{C_k}{U_s}$ if there was a previous request. A Constant Bandwidth Server (CBS) is also a dynamic server which uses a budget based system. It assigns each incoming task request a deadline, if the task uses the entire budget capacity it will be replenished again to be able to continue executing or be ready for the next request. When the budget is replenished the deadline is also postponed. The server has a server period of $T_s$, a server bandwidth of $U_s = \frac{Q_s}{T_s}$ where $Q_s$ is the server budget. This makes it impossible for the server bandwidth to become greater than $U_s$. This results in the task set always being schedulable with EDF. So the main difference between TBS and CBS is that CBS uses a budget mechanism to make sure the server bandwidth does not exceed a certain limit while the TBS does not.\\



        